CdGF_aucrf

### 2016-10-04 code/CdGF_AUCRF.Rmd
add partial dependence plots

## Can Day 0 Community members predict C. difficile CFU?
```{r fig.height= 10, fig.width=10}

@@

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 100316
n_trees <- 2001
iters <- 100
n_features <- 30
```

@@

```{r fig.width=8, fig.height=8, results= 'hide'}
#create dataframe for RF-classification
meta_file$Euth_Early <- factor(ifelse(meta_file[ , 'Early_Euth'] == FALSE, 1, 0))

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])

aucrf_data <- Predict_early_euth_df[,c('Euth_Early',rf_early_aucrf$Xopt)]

@@

#### leave-one-cage-out
LOcO_df <- Predict_df %>% 
                select(Euth_Early, cage_id, one_of(rf_early_aucrf$Xopt))
cage_list <- as.character(unique(LOcO_df$cage_id))

LOcO_probs <- c()
for(i in 1:length(cage_list)){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[!by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[LOcO_df$cage_id == cage_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOcO_roc <- roc(LOcO_df$Euth_Early~LOcO_probs)

@@

```{r fig.width=10, fig.height=10}

#Importance Plot
euth_otus <- rf_early_aucrf$Xopt
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

@@

>>>>

## Can Day 0 Community members predict C. difficile CFU?
```{r setup data, fig.height= 10, fig.width=10}

@@

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 1
n_trees <- 2001
iters <- 100
n_features <- 30
```

@@

```{r roc, fig.width=8, fig.height=8, results= 'hide'}
#create dataframe for RF-classification
meta_file$Euth_Early <- factor(ifelse(meta_file[ , 'Early_Euth'] == FALSE, 1, 0))

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
euth_otus <- rf_early_aucrf$Xopt

aucrf_data <- Predict_early_euth_df[,c('Euth_Early',euth_otus)]

@@

#### leave-one-cage-out
LOcO_df <- Predict_df %>% 
                select(Euth_Early, cage_id, one_of(euth_otus))
cage_list <- as.character(unique(LOcO_df$cage_id))

LOcO_probs <- c()
LOcO_rf <- c()
for(i in 1:length(cage_list)){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[!by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_rf[[i]] <- temp_model$RFopt
  LOcO_probs[LOcO_df$cage_id == cage_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOcO_roc <- roc(LOcO_df$Euth_Early~LOcO_probs)

@@

```{r importance, fig.width=10, fig.height=10}

#Importance Plot
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

### Partial Dependency Plots
###### Using optimal RF model generated from whole dataset

```{r partial dependence, fig.width=10, fig.height=10}
layout(matrix(c(1:20), nrow=5, byrow=TRUE))

for (i in seq_along(euth_otus)) {
  partialPlot(rf_early_aucrf$RFopt, aucrf_data, euth_otus[i], xlab='',
                main=paste(euth_tax$tax_label[i]))
}

```

@@

* Of note, I tried a few different seeds, and one otu (Turicibacter OTU 120) was identified as a classifier of cage/inocula but wasnt in others and was identified as a classifier of Euthanization. Also we occasionally lose OTU 50 as a classifier
